---
title: "NOAA_Data_request"
author: "Montana McLeod"
date: "7/8/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Specimen
```{r}
https://www.nwfsc.noaa.gov/data/api/v1/source/trawl.individual_fact/selection.csv?
  filters=project=Groundfish Slope and Shelf Combination Survey,
year>2014,year<2016
&variables=project,
trawl_id,
operation_dim$operation_type,
latitude_dd,
longitude_dd,
best_available_taxonomy_dim$grp_reg_depth_category,
best_available_taxonomy_dim$order_40,scientific_name,c
ommon_name,
partition,
length_cm,
length_type,
width_cm,
width_type,
net_touchdown_time,
net_liftoff_time,
sampling_start_hhmmss,
sampling_end_hhmmss,
depth_m,
year,
year_stn_invalid
```


# Haul
```{r}
https://www.nwfsc.noaa.gov/data/api/v1/source/trawl.operation_haul_fact/selection.csv?
  filters=project=Groundfish Slope and Shelf Combination Survey,
year>2014,year<2016
&variables=project,
trawl_id,
operation_dim$operation_type,
performance,
latitude_dd,
longitude_dd,
year,
date_yyyymmdd,
depth_m,
temperature_at_gear_c_der,
o2_at_gear_ml_per_l_der,
year_stn_invalid
```

# By species for 2009 - 2019
## greenstriped
```{r}
https://www.nwfsc.noaa.gov/data/api/v1/source/trawl.individual_fact/selection.csv?
filters=year>2008,year<2019,
project=Groundfish Slope and Shelf Combination Survey,
common_name= greenstriped rockfish,
&variables=project,
trawl_id,
operation_dim$operation_type,
latitude_dd,
longitude_dd,
best_available_taxonomy_dim$grp_reg_depth_category,
best_available_taxonomy_dim$order_40,scientific_name,
common_name,
partition,
length_cm,
length_type,
net_touchdown_time,
net_liftoff_time,
sampling_start_hhmmss,
sampling_end_hhmmss,
depth_m,
year,
year_stn_invalid
```
https://www.nwfsc.noaa.gov/data/api/v1/source/trawl.individual_fact/selection.csv?filters=year>2009,year<2019,project=Groundfish Slope and Shelf Combination Survey,common_name=greenstriped rockfish,&variables=project,trawl_id,operation_dim$operation_type,latitude_dd,longitude_dd,best_available_taxonomy_dim$grp_reg_depth_category,best_available_taxonomy_dim$order_40,scientific_name,common_name,partition,length_cm,length_type,net_touchdown_time,net_liftoff_time,sampling_start_hhmmss,sampling_end_hhmmss,depth_m,year,year_stn_invalid


